Xor-Some Preregistered Study: Preprocessing

### 2021-11-06 analysis/main/01_xor-some_prereg_preprocessing_final.Rmd
fix lang exclusion, check comprehension questions

Apply language related exclusion criterion:
Check native languages. Participants not indicating English as (one of) their native language(s) are excluded. We also compute some participant demographics.
```{r languages}
d %>% distinct(languages)
cat("Number of participants before excluding non-natives: ", d %>% distinct(submission_id) %>% count() %>% pull() ) 
# exclude non-natives if necessary
d_native <- d %>% 
 # filter(("en" | "En" | "bri") %in% languages)
  filter(grepl("[(en)(br)]", languages, ignore.case = T))

@@

>>>>

Apply language related exclusion criterion:
Check native languages. Participants not indicating English as (one of) their native language(s) are excluded. We also compute some participant demographics.
```{r languages}
d %>% distinct(languages)
cat("Number of participants before excluding non-natives: ", d %>% distinct(submission_id) %>% count() %>% pull() ) 
# exclude non-natives if necessary
d_native <- d %>% 
 # filter(("en" | "En" | "bri") %in% languages)
  filter(grepl("eng", languages, ignore.case = T))

@@

Investigate if the comprehension questions received expected responses on by-question basis:
```{r}
d_test %>% group_by(ID, test_question) %>% 
  mutate(
    expected = case_when( test_condition == "true" ~ 100,
                          test_condition == "false" ~ 0,
                          TRUE ~ 50)
  ) %>%
  summarise(
    expected = mean(expected),
    response = mean(response),
    difference = abs(expected - response)
  ) %>% 
  arrange(., desc(difference))

# look at the vignette text and the qeustion of the worst performing item
d_test %>% filter(ID == 64, test_question == "test_false1") %>% select(prompt, QUD) %>% View()
```
